% Autogenerated translation of about.md by Texpad
% To stop this file being overwritten during the typeset process, please move or remove this header

\documentclass[12pt]{book}
\usepackage{graphicx}
\usepackage{fontspec}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,left=.5in,right=.5in,top=.3in,bottom=0.3in]{geometry}
\setlength\parindent{0pt}
\setlength{\parskip}{\baselineskip}
\setmainfont{Helvetica Neue}
\usepackage{hyperref}
\pagestyle{plain}
\begin{document}

+++

\chapter*{About/Biography widget.}

widget = "about"
active = true
date = 2016-04-20T00:00:00

\chapter*{Order that this section will appear in.}

weight = 1

\chapter*{List your academic interests.}

[interests]
  interests = [
    "Computer Architecture",
    "Microarchitecture Design",
    "Machine Learning"
  ]

\chapter*{List your qualifications (such as academic degrees).}

[[education.courses]]
  course = "Doctor of Philosophy in Computer Science"
  institution = "Georgia Institute of Technology"
  year = 2019

[[education.courses]]
  course = "Master of Business Administration"
  institution = "Georgia Institute of Technology"
  year = 2019

[[education.courses]]
  course = "Master of Science in  Electrical and Computer Engineering"
  institution = "The University of Texas at Austin"
  year = 2014

 [[education.courses]]
  course = "Bachelor of Technology in Electrical Engineering"
  institution = "Indian Institute of Technology (IIT) Ropar"
  year = 2012

+++

\chapter*{Biography}

Divya Mahajan is a PhD candidate in the Computer Science Department at \href{https://www.gatech.edu/}{Georgia Institute of Technology} where she is advised by Professor \href{https://www.cc.gatech.edu/~hadi/}{Hadi Esmaeilzadeh}. She received her Bachelors (2012) in Electrical Engineering from \href{www.iitrpr.ac.in/}{Indian Institute of Technology Ropar}, India where she was honored with the President of India Gold medal for her outstanding academic performance. Subsequently, she completed her Masters (2014) from the \href{https://www.utexas.edu}{University of Texas, at Austin} in Electrical and Computer Engineering. 

She joined her PhD studies in Fall 2014 and since has been a part of \href{http://act-lab.org}{Alternate Computing Technologies lab}. Her research interests include computer architecture, microarchitecture design, and developing alternative technologies for efficient computing. She is continuously working towards designing full stack solutions and template-based architectures for accelerating Machine Learning and Deep Learning algorithms on an FPGA. She owns the very first open-source \href{http://act-lab.org/artifacts/tabla/}{hardware platform} for acceleration of data analytics. Besides her primary research-area of computer architecture, she has also worked at the intersection of machine learning, hardware design, programming languages and databases.

\end{document}
